### 2016-05-19 paper/paper.tex
edit pass through difficulty adjustment. am i understanding it correctly?

>>>>

\subsubsection{Difficulty Adjustment}

The difficulty of proof-of-work changes dynamically in DDoSCoin, as it does in
other crypto-currencies, in order to limit the rate at which new blocks are mined.
However, in DDoSCoin, the difficulty is adjusted separately for each target domain. 
Each victim domain has its own difficulty since domains could have different maximum throughputs, 
allowing more or fewer connections from all miners over the same time period. Consider
a single domain that handles many connections per second added to the target list. 
The miners would connect to that server more often, since it will give more chances 
at mining a block, and thus relieve traffic from the other targets.

DDoSCoin adjusts diffuculty for a given domain by looking at the past
BLOCK\_ADJUST blocks, and counting the number of blocks mined against
the given domain. This ratio is compared to the expected ratio based on the
current size of the victim list. If more blocks were mined than expected, the
difficulty for this domain is increased. Similarly, if fewer blocks were mined,
the difficulty for the domain is decreased.
This mechanism allows target domains that somehow become more
difficult to reach to quickly return to a more appropriate difficulty, without
having to wait for many blocks mined at the high difficulty.

At the same time, there is a global difficulty adjustment factor applied to all
domain difficulties that is computed based only on the number of blocks mined
over a given time. If blocks are being produced faster than expected, then the
difficulty on all blocks increases. Likewise, blocks coming in slower than
expected will reduce the global difficulty.

%This comes at a
%sacrifice to the agility of co when a domain has too low of a
%difficulty. This allows a run on an easily mined domain to occur for longer.
%

%We correct for this lower reactivity by dividing the number of blocks required 
%for a difficulty adjustment by the number of domains being targeted. Thus, as 
%more domains are in the target list and it becomes more likely that one may
%be able to handle many requests, the total number of mined blocks that will result
%in difficulty adjustment shrinks.

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level.
